\textbf{Using the MSU Thesis Class}

### 2024-05-17 docs/msu-thesis.tex
Updated annotated template file; updated new line in TOC entries to be more general

\begin{quote}
|\setcounter{msutocdepth}{0}|
\end{quote}
\subsubsection{Ensuring the minimum number of leader dots}
If your chapter titles are very long, they sometimes fail to put any leader dots before the page number in the Table of Contents. The thesis office requires a minimum of three dots of leaders for any TOC line. You can solve this problem by putting a line break  into the TOC entry title. To do this, use the optional argument of the corresponding |\chapter| or |\section| etc. command. Note that the line break needs to be preceded by |\protect|.

>>>>

\begin{quote}
|\setcounter{msutocdepth}{0}|
\end{quote}
\subsubsection{Adding line breaks to TOC entries}
If your chapter titles are very long, they sometimes fail to put any leader dots before the page number in the Table of Contents or they hyphenate a word in the title. The thesis office requires a minimum of three dots of leaders for any TOC line, and they don't seem to like hyphenation inside TOC entries.  You can solve both of these problems by putting a line break  into the TOC entry title. To do this, use the optional argument of the corresponding |\chapter| or |\section| etc. command. Note that the line break needs to be preceded by |\protect|.
